Scottish Child Poverty Briefing Plots

### 2024-06-13 minos/outcomes/ChildPovReduction_Combined.Rmd
Small changed to plotting scripts

---
title: "Scottish Child Poverty Briefing Plots"
output:
  pdf_document:
    toc: true
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

@@

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                   scen.list = scen.list.rel)
```

@@

```{r}
SF12_change_simple(summary_group = 'families',
                       scen.list = scen.list.rel)
```

@@

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                       scen.list = scen.list.abs)
```

@@

```{r}
SF12_change_simple(summary_group = 'families',
                       scen.list = scen.list.abs)
```

>>>>

---
title: "Scottish Child Poverty Briefing Plots"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
  pdf_document:
    toc: true
---

@@

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r "mental_illness_risk_plots", include=FALSE}
mental_illness_risk_counts <- function(summary_group, scen.list) {
  tit <- ' '
  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }

  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
  # summary_group <- 'men_illness_risk'

  # plot_data <- data %>%
  #   group_by(scen, year, mental_health_risk) %>%
  #   summarise(count = mean(count)) %>%
  #   filter(mental_health_risk == 'TRUE')
  # 
  # ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
  #   geom_point() +
  #   geom_line()
  mutate(num_priority_groups = case_when(
        num_priority_groups == 0 ~ 0,
        num_priority_groups == 1 ~ 1,
        num_priority_groups == 2 ~ 2,
        num_priority_groups >= 3 ~ 3)) %>%

  plot_data_2 <- data %>%
    filter(mental_health_risk == 'TRUE') %>%
    select(-prop, -mental_health_risk) %>%
    pivot_wider(names_from = scen,
                values_from = count) %>%
    rename(intervention = contains(scen.list[[1]]))
    mutate(MHR_diff = ChildPovertyReductionRELATIVE_2 - baseline) %>%
    select(run_id, year, MHR_diff) %>%
    group_by(year) %>%
    summarise(MHR_diff = mean(MHR_diff))

  p1 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
    geom_point() +
    geom_line() +
    labs(title = "Count of individuals at risk of mental health issues",
         subtitle = 'Intervention - Baseline') +
    xlab('Year') +
    ylab('Count')

  print(p1)
}
```

@@

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                   scen.list = scen.list.rel)

# mental_illness_risk_counts(summary_group = 'men_illness_risk',
#                            scen.list = scen.list.rel)
```

@@

```{r}
SF12_change_simple(summary_group = 'families',
                       scen.list = scen.list.rel)

# mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
#                            scen.list = scen.list.rel)
```

@@

```{r}
SF12_change_simple(summary_group = 'whole_pop',
                       scen.list = scen.list.abs)

# mental_illness_risk_counts(summary_group = 'men_illness_risk',
#                            scen.list = scen.list.abs)
```

@@

```{r}
SF12_change_simple(summary_group = 'families',
                       scen.list = scen.list.abs)

# mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
#                            scen.list = scen.list.abs)
```

### 2024-06-13 minos/outcomes/ChildPovReduction_plots.Rmd
Small changed to plotting scripts

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old6/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
#scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

@@

inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.test)
```

@@

inequality_plots(summary_group = 'families',
                 scen.list = scen.list.test)
```

@@

scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
summary_group <- 'men_illness_risk'

plot_data <- data %>%
  group_by(scen, year, mental_health_risk) %>%
  summarise(count = mean(count)) %>%
  filter(mental_health_risk == 'TRUE')

ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
  geom_point() +
  geom_line()

ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
  geom_point() +
  geom_line()

>>>>

#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/scp_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/Minos/output/default_config/cpr_summary_out/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/SCP_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/"
#workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old7_scot/"
workingDir <- "/home/luke/Documents/WORK/MINOS/CPR_ARC_SUMMARIES/old/old8_scot/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

@@

```{r "mental_illness_risk", include=FALSE}
mental_illness_risk_counts <- function(summary_group, scen.list) {
  tit <- ' '
  if (summary_group == 'men_illness_risk') { tit <- 'Whole Population' }
  if (summary_group == 'men_illness_risk_families') { tit <- 'Families' }

  # scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
  # summary_group <- 'men_illness_risk'

  # plot_data <- data %>%
  #   group_by(scen, year, mental_health_risk) %>%
  #   summarise(count = mean(count)) %>%
  #   filter(mental_health_risk == 'TRUE')
  # 
  # ggplot(plot_data, aes(x = year, y = count, group = scen, color = scen)) +
  #   geom_point() +
  #   geom_line()

  p1 <- ggplot(data = plot_data_2, aes(x = year, y = MHR_diff)) +
    geom_point() +
    geom_line()

  print(p1)
}
```

```{r}
scen.list.test <- c('baseline', 'ChildPovertyReductionRELATIVE_2')
#scen.list.test <- c('baseline', 'ChildPovertyReductionABSOLUTE')
#scen.list.test <- c('baseline', 'ChildPovertyReductionSUSTAIN')
whole_pop_data <- do.call(rbind, generate_df_list('whole_pop', scen.list.test))
```

@@

inequality_plots(summary_group = 'whole_pop',
                 scen.list = scen.list.test)

mental_illness_risk_counts(summary_group = 'men_illness_risk',
                           scen.list = scen.list.test)
```

@@

inequality_plots(summary_group = 'families',
                 scen.list = scen.list.test)

mental_illness_risk_counts(summary_group = 'men_illness_risk_families',
                           scen.list = scen.list.test)
```

@@
